Video Understanding : A review of action detection-recognition dataset

### 2024-02-26 paper.tex

\subsection{Charades}
Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
\subsection{Something Something}
Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects. 
\subsection{Kinetics}
In 2017, one of the most famous action classification datasets, Kinetics, was introduced. Its method combines elements from the previous HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}datasets and expands the number of action classes to 400. By collecting videos from YouTube, the dataset can capture various camera motions, angles, lighting conditions, etc., and therefore covering a broad range of human actions.

Later in 2018, an updated version, Kinetics-600, was introduced. Kinetics-600 is a superset of Kinetics-400, retaining the original 368 classes and splitting 32 classes to provide clearer explanations. Additionally, a new filtering method was used to gather videos correlated to the action classes. Due to some validation sets from Kinetics-400 becoming part of the Kinetics-600 test set, it is recommended not to evaluate Kinetics-600 with a pre-trained Kinetics-400 model.

In 2020, Kinetics-700-2020 was introduced, expanding by 30\% compared to Kinetics-600. Additional actions were sourced partly from EPIC-Kitchens and AVA datasets. Rare actions were gathered from more videos, and duplicated videos were removed. These changes resulted in a more balanced dataset.

@@

\subsection{AVA}
Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

@@

\subsection{EPIC-KITCHENS}
Since its first introduction in 2018, EPIC-KITCHENS (2020) now extends to provide a fully version of a large-scale egocentric dataset. Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{somethingsomething} and Hollywood in Home \cite{Charades}. However, this practice also leads to a lack of natural actions in real life. Given that situation, EPIC-KITCHENS captures random multitasking actions performed by real individuals without any scripts. By recording daily kitchen activities from the first-person perspective of 32 participants from 10 different countries, it aims to present a challenging real-life scenario.

@@

After the filtering process, the dataset has a total of more than 800K videos from over the world, demonstrating 887 classes. The labels follow hierarchy structure from general to particular action for studying various aspects of action performance.
\subsection{TinyVIRAT}
\subsection{ToyotaSmarthome}
\subsection{FineAction}
\section{Analysis}
Các thông tin ở từng mục sẽ được nói kĩ nhưng không đi sâu vào từng bộ dữ liệu mà mang tính tổng quát, sau đó thống kê vào bảng. Thông tin trên bảng sẽ được điền dạng kí hiệu hoặc yes/no, sau đó chú thích bên dưới.

>>>>

\subsection{Charades}
Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something \cite{Some} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
\subsection{Something Something}
Introduced its first version in 2017, Something V1 \cite{SomethingV1} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects.
\subsection{Multi-THUMOS}
Expanding upon the THUMOS \cite{THUMOS} dataset, Multi-THUMOS \cite{Multi-THUMOS} represents a substantial advancement in action recognition datasets, offering multi-action sequences over time. Addressing limitations observed in previous datasets like UCF101 \cite{UCF101} and HMDB51 \cite{HMDB51}, as well as its precursor THUMOS, Multi-THUMOS provides dense multilabel annotations of fined-grained actions for untrimmed video footage, therefore enhancing the accurately localizing in multi-action reasoning.

Overall, Multi-THUMOS contains a total of 30 hours from 413 videos, demonstrating 65 action classes and 38,690 annotations. Those classes are expanded from the original THUMOS and are arranged in a hierarchical relationship. Inside that, instance actions last on average 3.3 seconds, with the shortest action in this dataset (throw) lasting 66 milliseconds. Each video in Multi-THUMOS can contain up to 25 action labels, with a maximum of 9 actions per frame, significantly improved from 3 action labels, with a maximum of 2 actions per frame from THUMOS. 
\subsection{Kinetics}
In 2017, one of the most famous action classification datasets, Kinetics \cite{Kinetics-400}, was introduced. Its method combines elements from the previous HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}datasets and expands the number of action classes to 400. By collecting videos from YouTube, the dataset can capture various camera motions, angles, lighting conditions, etc., and therefore covering a broad range of human actions.

Later in 2018, an updated version, Kinetics-600 \cite{Kinetics-600}, was introduced. Kinetics-600 is a superset of Kinetics-400, retaining the original 368 classes and splitting 32 classes to provide clearer explanations. Additionally, a new filtering method was used to gather videos correlated to the action classes. Due to some validation sets from Kinetics-400 becoming part of the Kinetics-600 test set, it is recommended not to evaluate Kinetics-600 with a pre-trained Kinetics-400 model.

In the next year, Kinetics-700 \cite{Kinetics-700} was added, expanding by 30\% compared to Kinetics-600. Additional actions were sourced partly from EPIC-Kitchens and AVA datasets, and some were split from previous action classes for more fine-grained information. Because of serving as an expansion, it is recommended to train on Kinetics-600 and then evaluate on Kinetics-700 to ensure the unseen results.

In 2020, the final version Kinetics-700-2020 \cite{Kinetics-700-2020} was introduced. It keeps the same action classes as the 700 version but increase the dataset's quality. Geographical diversity are increased, rare actions were gathered from more videos, and duplicated videos were removed. These changes resulted in a more balanced dataset.

@@

\subsection{AVA}
Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{SomethingV1}, and Moments in Time \cite{MomentsinTime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

@@

\subsection{EPIC-KITCHENS}
Since its first introduction in 2018, EPIC-KITCHENS-100 \cite{EPIC-KITCHENS} now extends to provide a fully version of a large-scale egocentric dataset. Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{SomethingV1} and Hollywood in Home \cite{Charades}. However, this practice also leads to a lack of natural actions in real life. Given that situation, EPIC-KITCHENS captures random multitasking actions performed by real individuals without any scripts. By recording daily kitchen activities from the first-person perspective of 32 participants from 10 different countries, it aims to present a challenging real-life scenario.

@@

After the filtering process, the dataset has a total of more than 800K videos from over the world, demonstrating 887 classes. The labels follow hierarchy structure from general to particular action for studying various aspects of action performance.
\subsection{FineAction}
Introduced in 2022, FineAction \cite{FineAction} aims to create a novel large-scale and fine-grained video dataset specialized in the temporal action localization task. Recently, many datasets have provided a diversity of temporal annotations such as ActivityNet \cite{ActivityNet}, Multi-THUMOS \cite{Multi-THUMOS}, and HACS \cite{HACS}; however, they lack detailed fine-grained annotations for daily activities. Hence, FineAction aims to address the weaknesses of those datasets and reduce annotation bias to ensure generalization. It also proposes a new challenge of fine-grained localization.

FineAction provides 16,732 untrimmed videos of 106 action categories, containing up to 103,324 temporal instances. The action classes are arranged in a three-level granularity of taxonomy hierarchy. At the top level, the dataset demonstrates coarse-grained actions, while at the bottom, it presents fine-grained ones. Each clip has an average duration of 7.1 seconds. Up to 11.5\% of the clips have multiple action labels with overlaps.
\subsection{Toyota Smarthome}
Toyota Smarthome \cite{ToyotaSmarthome} is introduced to provide a realistic daily action dataset captured by security cameras. Its purpose is to address the limitation of action generalization from UCF101 \cite{UCF101}, HMDB51 \cite{HMDB51}, and Kinetics \cite{Kinetics-400} when they can't demonstrate fine-grained daily living activities. Therefore, the dataset provides a diversity of both fine-grained and composite actions, performed by uninstructed actors.

The dataset consists of 31 daily living activities performed by 18 actors, resulting in 16,115 videos. The actions are acted randomly with no script provided, resulting in untrimmed videos for localization. Each action can have multiple camera views, ranging from 2 to 7. For action recognition, the number of video clips per activity spreads from the rarest action (cutting bread with 45 clips) to the most frequent action (walking with 4070 clips). Each action can have a variety of durations, from a few seconds (sitting down) to a few minutes (cleaning dishes).
\section{Analysis}
Các thông tin ở từng mục sẽ được nói kĩ nhưng không đi sâu vào từng bộ dữ liệu mà mang tính tổng quát, sau đó thống kê vào bảng. Thông tin trên bảng sẽ được điền dạng kí hiệu hoặc yes/no, sau đó chú thích bên dưới.
